\chapter{AI900 Study Questions}
\resetquestioncounter{}
\begin{qanda}
	\begin{question}
What is the primary purpose of text preprocessing in NLP?
	\end{question}
	\begin{answer}
To transform raw text into an analyzable form.
	\end{answer}
\end{qanda}

\begin{qanda}
	\begin{question}
What does tokenization in NLP refer to?
	\end{question}
	\begin{answer}
Breaking text into smaller chunks or tokens.
	\end{answer}
\end{qanda}

\begin{qanda}
	\begin{question}
Which of the following is considered an out-of-vocabulary word?
	\end{question}
	\begin{answer}
A word that is not found in the text corpus's vocabulary.
	\end{answer}
\end{qanda}

\begin{qanda}
	\begin{question}
What is the goal of stemming in text preprocessing?
	\end{question}
	\begin{answer}
To reduce words to their root form.
	\end{answer}
\end{qanda}

\begin{qanda}
	\begin{question}
Which preprocessing step involves removing commonly used words that usually have little value in the text?
	\end{question}
	\begin{answer}
Stop word removal.
	\end{answer}
\end{qanda}

\begin{qanda}
	\begin{question}
Which Azure AI service provides text analysis capabilities?
	\end{question}
	\begin{answer}
Azure AI Language Service
	\end{answer}
\end{qanda}

\begin{qanda}
	\begin{question}
How do you add functionality to a Conversational Language Understanding app in Language Studio?
	\end{question}
	\begin{answer}
By adding intents, entities, and utterances.
	\end{answer}
\end{qanda}

\begin{qanda}
	\begin{question}
What is the final step in testing a deployed Conversational Language Understanding model in Language Studio?
	\end{question}
	\begin{answer}
Submitting text commands and reviewing the predicted intents and entities.
	\end{answer}
\end{qanda}

\begin{qanda}
	\begin{question}
What is the first step in using Azure AI Speech Studio for speech to text transcription?
	\end{question}
	\begin{answer}
Creating an Azure AI Speech resource.
	\end{answer}
\end{qanda}

\begin{qanda}
	\begin{question}
What is the primary function of the Azure AI Speech service?
	\end{question}
	\begin{answer}
To transcribe speech into text and vice versa.
	\end{answer}
\end{qanda}

\begin{qanda}
	\begin{question}
What is the difference between stemming and lemmatization?
	\end{question}
	\begin{answer}
Stemming changes words into a root form; lemmatization changes words into their base or dictionary form.  Stemming is faster and simpler than lemmatization, which requires understanding of the context.
	\end{answer}
\end{qanda}

\begin{qanda}
	\begin{question}
What is Bag of Words (BoW) in NLP?
	\end{question}
	\begin{answer}
A technique for converting text into numerical feature vectors.
	\end{answer}
\end{qanda}

\begin{qanda}
	\begin{question}
In the context of NLP, what does 'corpus' refer to?
	\end{question}
	\begin{answer}
A collection of text documents.
	\end{answer}
\end{qanda}

\begin{qanda}
	\begin{question}
Why is text vectorization necessary in NLP?
	\end{question}
	\begin{answer}
To convert text into a numerical format that machine learning algorithms can process.
	\end{answer}
\end{qanda}

\begin{qanda}
	\begin{question}
What does TF-IDF stand for in text processing?
	\end{question}
	\begin{answer}
Term Frequency-Inverse Document Frequency.
	\end{answer}
\end{qanda}

\begin{qanda}
	\begin{question}
What is the purpose of sentiment analysis in NLP?
	\end{question}
	\begin{answer}
To determine the emotional tone behind a body of text.
	\end{answer}
\end{qanda}

\begin{qanda}
	\begin{question}
Which Azure AI feature enables the translation of spoken language into text?
	\end{question}
	\begin{answer}
Speech-to-Text
	\end{answer}
\end{qanda}

\begin{qanda}
	\begin{question}
Which feature of Language Understanding (LUIS) allows it to identify the intention behind a sentence?
	\end{question}
	\begin{answer}
Intent recognition.
	\end{answer}
\end{qanda}

\begin{qanda}
	\begin{question}
Which Azure AI feature is specifically mentioned for extracting semantic meaning from text?
	\end{question}
	\begin{answer}
NLP capabilities.
	\end{answer}
\end{qanda}

\begin{qanda}
	\begin{question}
How can you enable a Language resource for use in Language Studio?
	\end{question}
	\begin{answer}
By enabling Managed identity.
	\end{answer}
\end{qanda}

\begin{qanda}
	\begin{question}
How does TF-IDF work to prioritize words in a document?
	\end{question}
	\begin{answer}
By increasing the score of words that appear frequently in a particular document but less so in the corpus.
	\end{answer}
\end{qanda}

\begin{qanda}
	\begin{question}
What challenge does sarcasm pose in NLP?
	\end{question}
	\begin{answer}
It often requires advanced AI models to understand.
	\end{answer}
\end{qanda}

\begin{qanda}
	\begin{question}
Why is context important in processing homonyms in NLP?
	\end{question}
	\begin{answer}
It is crucial for determining the correct meaning of a word based on usage.
	\end{answer}
\end{qanda}

\begin{qanda}
	\begin{question}
What problem does the presence of colloquialisms and slang pose for NLP systems?
	\end{question}
	\begin{answer}
They introduce variability and informality that can be difficult to interpret.
	\end{answer}
\end{qanda}

\begin{qanda}
	\begin{question}
In the classical NLP pipeline, what is the sequence of steps for processing text data?
	\end{question}
	\begin{answer}
Text Preprocessing $\rightarrow{}$ Text Vectorization $\rightarrow{}$ Machine Learning Predictions.
	\end{answer}
\end{qanda}

\begin{qanda}
	\begin{question}
What is conversational AI?
	\end{question}
	\begin{answer}
A form of AI where an agent engages in a dialogue with a human.
	\end{answer}
\end{qanda}

\begin{qanda}
	\begin{question}
Which process involves identifying the main subjects and entities in a text document?
	\end{question}
	\begin{answer}
Text analysis.
	\end{answer}
\end{qanda}

\begin{qanda}
	\begin{question}
How does Azure AI Language Service enhance conversational bots?
	\end{question}
	\begin{answer}
By enabling language understanding and question answering.
	\end{answer}
\end{qanda}

\begin{qanda}
	\begin{question}
In QnA Maker, what is the role of the knowledge base?
	\end{question}
	\begin{answer}
To store FAQs and other information for answering user questions.
	\end{answer}
\end{qanda}

\begin{qanda}
	\begin{question}
What does the sentiment analysis output include for each analyzed sentence?
	\end{question}
	\begin{answer}
Scores next to positive, neutral, and negative categories.
	\end{answer}
\end{qanda}

\begin{qanda}
	\begin{question}
What is the role of word embeddings in understanding text for LLMs?
	\end{question}
	\begin{answer}
To represent text numerically in a vector space.
	\end{answer}
\end{qanda}

\begin{qanda}
	\begin{question}
Which term describes AI models capable of generating new data similar to the input data?
	\end{question}
	\begin{answer}
Generative Models
	\end{answer}
\end{qanda}

\begin{qanda}
	\begin{question}
What distinguishes Generative AI from Discriminative AI?
	\end{question}
	\begin{answer}
Generative AI creates new data, while Discriminative AI makes predictions based on existing data.
	\end{answer}
\end{qanda}

\begin{qanda}
	\begin{question}
To complete the sentence, select the appropriate option in the answer area. Data values that influence the prediction of a model are called \_\_\_\_\_?
	\end{question}
	\begin{answer}
Features.
	\end{answer}
\end{qanda}

\begin{qanda}
	\begin{question}
What does the prompt “Create an image of an elephant eating a hamburger” illustrate in Microsoft Copilot?
	\end{question}
	\begin{answer}
Image generation.
	\end{answer}
\end{qanda}

\begin{qanda}
	\begin{question}
Which playground feature allows you to experiment with natural language generation in Azure OpenAI Studio?
	\end{question}
	\begin{answer}
Chat playground.
	\end{answer}
\end{qanda}

\begin{qanda}
	\begin{question}
What is the primary function of the content filters in Azure OpenAI?
	\end{question}
	\begin{answer}
To prevent offensive output.
	\end{answer}
\end{qanda}

\begin{qanda}
	\begin{question}
What happens if you try to deploy multiple models in Azure OpenAI?
	\end{question}
	\begin{answer}
It leads to Quota and token related issues.
	\end{answer}
\end{qanda}

\begin{qanda}
	\begin{question}
In the Azure OpenAI Studio, where can you manage model deployments and data?
	\end{question}
	\begin{answer}
Models.
	\end{answer}
\end{qanda}

This is a poorly answered question.  What is a more complete answer?

\begin{qanda}
	\begin{question}
How does the Large Language Model (LLM) understand text?
	\end{question}
	\begin{answer}
By converting text into numeric word embeddings.
	\end{answer}
\end{qanda}

\begin{qanda}
	\begin{question}
Is there a numeric way to represent association between text or words?
	\end{question}
	\begin{answer}
Yes, through word embeddings in a vector space.
	\end{answer}
\end{qanda}

\begin{qanda}
	\begin{question}
What is the primary purpose of Generative AI in natural language processing?
	\end{question}
	\begin{answer}
Generating new content based on learned patterns.
	\end{answer}
\end{qanda}

\begin{qanda}
	\begin{question}
What are the allowable answers to this question?
	\end{question}
	\begin{answer}
By storing associations between words in a vector space.
	\end{answer}
\end{qanda}

\begin{qanda}
	\begin{question}
What is the main foundation for the Personal Digital Assistant?
	\end{question}
	\begin{answer}
Bot Framework.
	\end{answer}
\end{qanda}

\begin{qanda}
	\begin{question}
What is the primary step you should take after deploying an Azure OpenAI model to start using it?
	\end{question}
	\begin{answer}
Navigate to your deployed model.
	\end{answer}
\end{qanda}

\begin{qanda}
	\begin{question}
Which model is used for image generation in Azure OpenAI Service?
	\end{question}
	\begin{answer}
DALL-E.
	\end{answer}
\end{qanda}

\begin{qanda}
	\begin{question}
What are the four categories of potentially harmful content that content filters in Azure OpenAI Studio are based on?
	\end{question}
	\begin{answer}
Hate, Sexual, Violence, Self-harm.
	\end{answer}
\end{qanda}

\begin{qanda}
	\begin{question}
Which Azure service can be used for real-time monitoring and diagnostics of applications?
	\end{question}
	\begin{answer}
Azure Application Insights
	\end{answer}
\end{qanda}

\begin{qanda}
	\begin{question}
What is a key advantage of using generative AI models for text generation?
	\end{question}
	\begin{answer}
Capture of complex patterns and semantic relationships in textual data
	\end{answer}
\end{qanda}

\begin{qanda}
	\begin{question}
What process does LLM use to predict the next word in a sentence?
	\end{question}
	\begin{answer}
Leveraging learned associations and assigning importance scores.
	\end{answer}
\end{qanda}

\begin{qanda}
	\begin{question}
What role does self-supervised learning play in LLMs?
	\end{question}
	\begin{answer}
It enables LLMs to understand text by learning from unlabeled data
	\end{answer}
\end{qanda}

\begin{qanda}
	\begin{question}
You build a QnA Maker bot by using a frequently asked questions (FAQ) page.  You need to add professional greetings and other responses to make the bot more user friendly.  What should you do?
	\end{question}
	\begin{answer}
Add chit-chat
	\end{answer}
\end{qanda}

\begin{qanda}
	\begin{question}
You are developing a chatbot solution in Azure. Which service should you use to determine a user's intent?
	\end{question}
	\begin{answer}
Language Understanding (LUIS)
	\end{answer}
\end{qanda}

\begin{qanda}
	\begin{question}
A company employs a team of customer service agents to provide telephone and email support to customers.  The company develops a webchat bot to provide automated answers to common customer queries.  Which business benefit should the company expect as a result of creating the webchat bot solution?
	\end{question}
	\begin{answer}
A reduced workload for the customer service agents.
	\end{answer}
\end{qanda}

\begin{qanda}
	\begin{question}
You need to develop a chatbot for a website. The chatbot must answer users' questions based on the information in the following documents:
\begin{bulletedlist}
	\item A product troubleshooting guide in a Microsoft Word document
	\item A frequently asked questions (FAQ) list on a webpage
\end{bulletedlist}
Which service should you use to process the documents?
	\end{question}
	\begin{answer}
QnA Maker.
	\end{answer}
\end{qanda}

\begin{qanda}
	\begin{question}
You are building a Language Understanding model for an e-commerce business.  You need to ensure that the model detects when utterances are outside the intended scope of the model.  What should you do?
	\end{question}
	\begin{answer}
Add utterances to the None intent.
	\end{answer}
\end{qanda}

\begin{qanda}
	\begin{question}
Which of the following is not an offering of Cognitive Services?
\begin{bulletedlist}
	\item Language
	\item Speech recognition
	\item Vision
	\item 3D
\end{bulletedlist}
	\end{question}
	\begin{answer}
3D
	\end{answer}
\end{qanda}

\begin{qanda}
	\begin{question}

	\end{question}
	\begin{answer}

	\end{answer}
\end{qanda}

\begin{qanda}
	\begin{question}

	\end{question}
	\begin{answer}

	\end{answer}
\end{qanda}

